Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]

### 2013-09-18 snapshot_system/fast14_evaluation.tex
change to table

{\bf Throughput.}
Figure~\ref{fig:parallel_backup} shows the  backup throughput per each machine when all machine nodes 
handle  several VMs in parallel.
To begin, on each node we write snapshots for 4 VMs concurrently, and gradually 
increase number of VMs to 12 to saturate our system capability. We observed 
the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
which is far beyond our QFS file system capability. The reason behind it is our efficient
deduplication architecture and compression which greatly reduce the amount of data that needs to be written to
the file system. The main bottleneck here is that our QFS installation only
manages one disk per node, which prevents it from fully utilizing the the
benefits of parallel disk access. We expect our architecture can
perform even better in production clusters, which often have ten or more disks on each node.

\begin{table}
    \begin{tabular}{l|lll|lll}
    Num. of concurrent      & \multicolumn{2}{l}{Throughput without I/O throttling (MB/s)} & \multicolumn{2}{l}{Throughput with I/O throttling (MB/s)} \\
    backup streams per node & Raw                                       & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\
    1                       & 1369.6                                    & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
    2                       & 2408.5                                    & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
    4                       & 4101.8                                    & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
    6                       & 5456.5                                    & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
    \end{tabular}
\end{table}

>>>>

{\bf Throughput.}
Table~\ref{tab:throughput} shows the  backup throughput per each machine when all machine nodes 
handle  several VMs in parallel.
To begin, on each node we write snapshots for 4 VMs concurrently, and gradually 
increase number of VMs to 12 to saturate our system capability. We observed 
the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
which is far beyond our QFS file system capability. The reason behind it is our efficient
deduplication architecture and compression which greatly reduce the amount of data that needs to be written to
the file system. The main bottleneck here is that our QFS installation only
manages one disk per node, which prevents it from fully utilizing the the
benefits of parallel disk access. We expect our architecture can
perform even better in production clusters, which often have ten or more disks on each node.

\begin{table*}[t]
    \begin{tabular}{l|lll|lll}
    Num. of concurrent      & \multicolumn{3}{l}{Throughput without}   & \multicolumn{3}{l}{Throughput with} \\
    backup tasks per node & \multicolumn{3}{l}{I/O throttling (MB/s)} & \multicolumn{3}{l}{I/O throttling (MB/s)} \\ \hline
                            & Raw                                       & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\
    1                       & 1369.6                                    & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
    2                       & 2408.5                                    & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
    4                       & 4101.8                                    & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
    6                       & 5456.5                                    & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
    \end{tabular}
\caption{Backup throughput under different concurrency}
\label{tab:throughput}
\end{table*}
